Finite Property Convex Elicitation Paper

### 2019-01-24 jessie-writeup/jw-holes-clarified.tex
Gutted my writeup and cleaned it up

A set $\Theta \subseteq 2^{\R}$ is an unlabeled property, and finite if $|\Theta| < \infty$.
Note that $\R$ finite implies $\Theta$ is finite.
Observe that $\Theta$ is a set of level sets, and not a function.

@@

\begin{notation}
Let $\gamma: \P \toto\R'$ and $\Gamma: \P \toto\R$.
We say $\gamma \preceq \Gamma$ if for all $p \in \P$, we observe $\gamma(p) = \Gamma(p) \cap \R'$.

\jessie{Is there a better way to say this? ex: ``For all $r' \in \R'$, there is an $r\in \R$ such that $\Gamma_r = \gamma_{r'}$'' ... this suggests the properties are equivalent-ish.}
\end{notation}
\jessie{In the latter definition, if $\Gamma$ embeds $\gamma$, then $\gamma \preceq \Gamma$ since $\Gamma_{\varphi(r')} = \gamma_{r'}$ for all $r' \in \R'$.}

\begin{definition}
	The elicitable property $\Gamma:\P\toto \R$ is an \emph{embedding} of $\gamma: \P \toto \R'$ if there exists an injection $\varphi:\R' \to \R$ such that $\varphi(r) \in \Gamma(p) \iff r \in \gamma(p)$. 
\end{definition}

We slightly abuse notation to say that if $\Gamma$ is an embedding of $\gamma$, then $\gamma \preceq \Gamma$ if and only if $\varphi(\gamma(p)) = \Gamma(p) \cap \varphi(\R')$\footnote{If $S$ is a set and $\phi$ a function, we write $\phi(S) := \{ \phi(x) : x \in S \}$.}.
\jessiet{Do we want the above statement? Meh}

Note that we can take $\varphi^{-1}(r') = \{ r \in \R: \varphi(r) = r' \}$.
That is, we define the inverse of $\varphi$ as a possibly set-valued function.

\begin{definition}
A property $\Gamma: \P \toto \R$ is \emph{finite} if $\R$ is finite. % $\im(\Gamma) := \{r\in\Gamma(p) : p\in\P, r \in \R \} = \bigcup_{p\in\P} \Gamma(p)$ is a finite set.
\end{definition}

@@

\section{Conjectures and Lemmas on the way}

\begin{lemma}\label{lem:gam-prime-exists}
	Let $\Gamma:\P \toto \R$ be a nondegenerate elicitable property with a finite set of full-dimensional level sets $\Theta$ so that $\bigcup_{\theta \in \Theta}\theta = \P$.
	There exists a nondegenerate, nonredundant property $\gamma: \P \toto \R'$ such that $\gamma \preceq \Gamma$. 
\end{lemma}
\begin{proof}
	Construct the finite set $\R' = \{[r] \in \Gamma(p) : p \in \inter{\theta} \}_{\theta \in \Theta}$, where $[r]$ is one consistent report for all the reports $r, r'$ such that $\Gamma_r = \Gamma_{r'}$. 
	(If $\R'$ is not finite, choose just one $r \in \R$ so that $\theta = \Gamma_r$.)
	Defining the property $\gamma : p \mapsto \Gamma(p) \cap \R'$, we see that $\gamma \preceq \Gamma$.
	%Equivalently, we can observe for all $p \in \P$, that $\gamma(p) = \{ [r] : r \in \Gamma(p) \cap \R' \}$. %\jessie{Don't think this is necessary...?}
	We want to show that the constructed $\gamma$ is nondegenerate and nonredundant.

	As $\Gamma$ is nondegenerate, there is some report $r \in \R$ such that $r \in \Gamma(p)$, so $[r] \in \gamma(p)$ and is well-defined for all $p \in \P$.
	Therefore, $\gamma$ is nondegenerate.

	Now to see $\gamma$ is nonredundant, first consider two level sets $r_1, r_2$ such that $\Gamma_{r_1} = \Gamma_{r_2}$.
	In this case, $[r_1] = [r_2] = r'$, so $\gamma_{r'} = \gamma_{r'}$ does not lead to a redundant report.

	To see there are no reports $r, r'$ so that $\gamma_{r} \subsetneq \gamma_{r'}$, we use contradiction.
	Suppose there were such reports.
	By construction of $\R'$, we know both $\gamma_{r'}$ and $\gamma_r$ are full dimensional.
	\jessie{Here's where it gets hand-wavy}
	Therefore, we contradict convexity of the scoring rule $G$, since there is a bijection between the subgradients of $G$ and reports in $\R'$ (since we reduce to equivalent reports-- see Theorem~\ref{thm:bij-loss-to-score}).
	As $G$ is convex, it must be differentiable almost everywhere. 
	\jessiet{See Conjecture~\ref{conj:cvx-sets-nonempty-int-iff-pos-measure}}
	However, for every distribution in $\gamma_{r'} \cap \gamma_{r} = \gamma_{r'}$, the subgradient of $G$ is set-valued, and therefore $G$ is not differentiable on a set of positive Lebesgue measure in the simplex. 
	Contradicting the elicitability of $\gamma$, we conclude $\gamma$ is nonredundant.

%	\jessie{This next paragraph is definitely incomplete (HOLE)}
%	If $\gamma$ is redundant, then remove any redundant reports from $\R'$.
%	Any level set with a redundant report must either (a.) equal to another level set or (b.) a proper subset of another level set. 
%	We know that (a.) does not happen from the construction of $\R'$ using only one equivalent report per level set.
%	To see that (b.) does not happen, suppose for contradiction that $r_1, r_2 \in \R'$ so that $\gamma_{r_1}\subsetneq \gamma_{r_2}$.
%	Then we know that $\gamma_{r_1}$ must not be full dimensional \jessie{by argument from scoring rule $G$} and therefore, $\gamma_{r_1}$ must have empty interior.
%	However, if $\gamma_{r_1} = \Gamma_{r_1}$ has empty interior, then $r_1\not\in \R'$, so we observe a contradiction.
%	Thus, $\gamma$ is nonredundant.

@@

\begin{lemma}\label{lem:define-trim}
	Let $\Gamma:\P\toto\R$  be a nondegenerate, elicitable property with a finite set of level sets $\Theta$ so that $\bigcup_{\theta \in \Theta} \theta = \P$.
	There exists an unlabeled property $\Theta$ so that for all nondegenerate, nonredundant $\gamma \preceq \Gamma$, we have $\strip(\gamma) = \Theta := \trim(\Gamma)$.
\end{lemma}

\begin{proof}
	Let $\gamma:\P \toto \bar\R$ and $\Gamma' : \P \toto \R'$ be nondegenerate, nonredundant properties so that $\gamma \preceq \Gamma$ and $\Gamma'\preceq \Gamma$.
	We want to show $\strip(\gamma) = \strip(\Gamma')$ in order to conclude that $\trim(\Gamma)$ is well-defined.
	For each $\bar r \in \bar\R$, there is a set of reports in $S \subseteq \R$ so that there is a full-dimensional level set $\theta = \bigcap_{s\in S}\Gamma_s$ and $\bar r = [s]$ for every $s \in S$.
	For the same set of reports $S$, we can equivalently choose a different representative report $r' \in \R'$ so that $r' = [s]$ for every $s \in S$, since $\Gamma' \preceq \Gamma$.

	There is then a bijection $\varphi : \bar \R \to \R'$ so that $\varphi(\gamma(p)) = \Gamma'(p)$ for all $p \in \P$.
	Thus, the level sets of each report are the same since they are restrictions of the same property, so $\strip(\gamma) = \{ \gamma_r : r \in \bar \R \} = \{ \Gamma_r : r \in \bar \R \} = \{ \Gamma_{\varphi(r)} : r \in \bar \R \} = \{ \Gamma_r : r \in \R' \} = \strip(\Gamma')$.
\end{proof}

%\begin{conjecture}\label{conj:trim-full-dim}
%	Consider a nondegenerate, elicitable property $\Gamma$ with finitely many level sets.
%	Every $\theta \in \Theta := \trim(\Gamma)$ is full-dimensional  
%\end{conjecture}
%
%\begin{proof}
%	\jessie{Uses: Lemma~\ref{lem:gam-prime-exists}.}
%	
%	We define $\trim(\Gamma)$ in terms of the property $\gamma: \P \toto \R'$ such that $\gamma \preceq \Gamma$ and $\R'$ is as constructed in Lemma~\ref{lem:gam-prime-exists}.
%	For each $\theta \in \trim(\Gamma) = \strip(\gamma)$, there must be a report $r \in \R'$ such that $\theta = \gamma_r = \Gamma_{r}$.
%	By construction, $r \in \R' \implies \inter{\gamma_r} = \inter{\theta} \neq \emptyset$.
%	Since $\theta$ has nonempty interior, then $\theta$ is full dimensional. 
%\end{proof}

\begin{lemma}\label{lem:lev-sets-subsets}
	Let the property $\Gamma: \P \toto \R$ be elicitable and the nondegenerate, nonredundant property $\gamma: \P \toto \R'$ so that $\gamma \preceq \Gamma$.
	Then the level sets of $\Gamma$ are subsets of the level sets of $\gamma$.
\end{lemma}

\begin{proof}
	It is sufficient to show $\theta \in \strip(\Gamma) \implies \theta \in \strip(\gamma)$.
	Given $\theta \in \strip(\Gamma)$, there is some report $r \in \R$ so that $r \in \Gamma(p)$ for every $p \in \theta$.
	For every $r' \in \R'$, recall that there is an $r \in \R$ so that $r' = [r]$.
	By definition, $r \in \Gamma(p) \implies [r] = r' \in \gamma(p)$.
	Therefore, there is some $r' \in \R'$ so that $p \in \Gamma_r \implies p \in \Gamma_{[r]} = \gamma_{r'}$.
%	For every $r \in \reals^d$, there is some $r' \in \R$ so that $ p \in \theta = \Gamma_r = \{ p \in \P : r \in \Gamma(p) \} \subseteq \Gamma_{r'} \implies p \in \Gamma_{r'}$ in two cases.
%	
%	First, if $r \not \in \R$, it is a redundant report, so its level set is a subset or equal to another level set for a report in $\R$.
%	In the second case, for $r \in \R$, we know $p \in \Gamma_{r} \implies p \in \{ p \in \P : r \in \Gamma(p) \cap \R \} = \{ p \in \P : r \in \gamma(p) \} = \gamma_{r}$. 
\end{proof}

@@

  The following are equivalent:
  \begin{enumerate}
  \item There is a nondegenerate, finite property $\gamma:\P\toto\R'$ such that there is an injection $\varphi:\R'\to\reals^d$ such that $r\in\gamma(p) \iff \varphi(r) \in \Gamma(p)$. (i.e. $\Gamma$ embeds finite $\gamma$).

  \item There is a finite set of full dimensional level sets $\Theta$ of $\Gamma$ that union to $\P$.
  \item $\strip(\Gamma)$ is finite. \jessie{Seems like we could just make note of this-- not sure if it needs its own statement.}
  \item $\trim(\Gamma)$ is finite. 
  \item $\trim(\Gamma)$ is finite and elicitable. \jessie{IMO, we can cut}
  \end{enumerate}
\end{proposition}

\begin{proof}
We proceed in a cycle to show $4 \implies 1 \implies 5 \implies 2 \implies 3 \implies 4$.

\begin{enumerate}

\item[$4 \implies 1$] \jessiet{Cut}
Construct $\R' = \{ [r] \in \Gamma(p): p \in \inter{\theta} \}_{\theta\in\Theta}$ as in Lemma~\ref{lem:gam-prime-exists}.
Let $\varphi : \R' \to \reals^d$ be the identity and $\gamma := \Gamma|_{\R'}$.
Since $\trim(\Gamma)$ is finite, we then know $\R'$ is finite, and so $\gamma$ is a finite property.
We can then easily see that $r \in \gamma(r) \implies r \in \Gamma(p)$ as $\R' \subseteq \reals^d$.
Additionally, for any $r \in \R'$ so that $r \in \Gamma(p)$, we know that $r \in \Gamma|_{\R'} = \gamma$.
Therefore, $\Gamma$ embeds $\Gamma|_{\R'} = \gamma$.

%Since $\Gamma$ has a finite set of full-dimensional level sets comprising $\trim(\Gamma)$ that union to $\P$ (by nondegeneracy of $\Gamma$), we can apply Lemma~\ref{lem:gam-prime-exists} to observe there is a nondegenerate, nonredundant $\gamma \preceq \Gamma$, and we show $\Gamma$ embeds $\gamma$.
%First, we know $\gamma$ is finite as there is only one report $r \in \R'$ per full dimensional level set, of which we know there are finitely many since $\trim(\Gamma)$ is finite (as each level set in $\trim$ is full dimensional from Conjecture~\ref{conj:trim-full-dim}).

%For every $r' \in \R'$, let $\varphi(r') = \{ r\in\reals^d : r' = [r] \}$.
%Then clearly for all $r \in \Gamma(p)$, we know $[r] = r' \in \gamma(p)$.
%Additionally, we know that if $r' \in \gamma(p)$, then every equivalent report $r$ such that $[r] = r'$ as in $\Gamma(p)$, so $\Gamma$ embeds $\gamma$.
%\jessie{Circular logic...}

\item [$1 \implies 5$]
(Also shows $1 \implies 4$).

We know $\strip(\gamma) = \trim(\Gamma)$ \jessie{how...}, and as $\gamma$ is finite, so is $\strip(\gamma)$ since strip is generated from the (finite) report set.
Additionally, we know that $L|_{\R'}$ elicits $\trim(\Gamma)$ from \emph{cvx-fin-notes.tex}.

\item [$5 \implies 2$]
(Also $4 \implies 2$)

Since $\Gamma$ is nondegenerate and every $\theta \in \trim(\Gamma)$ is full dimensional, it is clear that the union of the (full-dimensional) level sets of $\trim(\Gamma)$ union to $\P$ by nondegneracy of $\Gamma$.

\item [$2 \implies 3$] \jessiet{Cut}
	We know there is a nonredundant, nondegenerate property $\gamma : \P \toto \R$ so that $\gamma \preceq \Gamma$ and therefore $\strip(\gamma) = \trim(\Gamma) = \Theta$ by Lemma~\ref{lem:gam-prime-exists} and the definition of trim (Lemma~\ref{lem:define-trim}).
	We then want to show $\strip(\Gamma) = \strip(\gamma) \bigcup S$, where $S$ is some finite set.
	Consider the level set $\Gamma_{r'}$ for $r' \in \reals^d$.
	If $r' \in \R$, then $\Gamma_{r'} \in \strip(\gamma)$.
	If $r' \not \in \R$, then there is a report $r \in \R$ so that the level set $\Gamma_{r'} \subseteq \Gamma_r = \gamma_r$ by Lemma~\ref{lem:lev-sets-subsets}, and we know that $\Gamma_{r'}$ has empty interior by the construction of $\R$ and nonredundancy of $\gamma$, as $\{p \in \P: \{r_1, r_2\} \in \gamma(p), [r_1] \neq [r_2] \}$ must have measure $0$ by the convexity of $G$.
	\jessie{Waving my hands at this again, but same argument as the proof of Conjecture 1.}

	We know this only happens at lower dimensional level sets $\theta$ since the optimal report is unique on the interior of level sets as $\gamma$ is nonredundant.
	That is, for all level sets $\theta$ and $p \in \inter \theta, |\partial G(p)| = 1$.
	Since $\theta$ is not full dimensional and there is only a finite set of full dimensional level sets at union to $\P$, we know there is a finite set of full dimensional level sets $\{\theta_i\}_{i=1}^m$ in the $\epsilon$-ball around each $p \in \theta$ so that for any $p_i \in \inter{\theta_i}$, we observe $\partial G(p_i) \neq \partial G(p_j)$ for all $i \neq j$ and there is a bijection $\varphi$ so that $\varphi(\partial G(p_i)) = \gamma(p_i) = \{r_i\}$ for all $1 \leq i \leq m$.
	Additionally, as level sets are closed, we claim $p \in \gamma_{r_i} \implies p \in \Gamma_{r_i}$ for all $1 \leq i \leq m$.
	Therefore, $p \in \theta \implies p \in \bigcap_{r' \in \{r_i\}_{i=1}^m} \gamma_{r'}\implies p \in \bigcap_{r' \in \{r_i\}_{i=1}^m} \Gamma_{r'}$ by closure of level sets for some $\{r_i\}_{i=1}^m \subseteq \R'$.
	As $\R'$ is finite, so is the power set $2^{\R'}$, so the set $S = \{\Gamma_r : r \in \reals^d \setminus \R \}$ is finite.
	Therefore $\strip(\Gamma) = \strip(\gamma) \bigcup S$ is finite.

\item [$3 \implies 4$]
\jessiet{Cut}
Since $\trim(\Gamma) \subseteq \strip(\Gamma)$, then the strip being finite implies the trim is finite.

\item[$2 \implies 1$]
\jessie{Only part needed if we decide to cut 3 and 5.}

Construct $\R' := \{[r] \in \Gamma(p) : p \in \inter{\theta} \}_{\theta \in \Theta}$.
The property $\gamma: p \mapsto \Gamma(p) \cap\R'$ is then finite as $\R'$ is finite.
Taking $\varphi$ to be the identity, we observe $\Gamma$ embeds this finite $\gamma$.
\end{enumerate}

@@

\section{Lemmas that probably aren't necessary to show in a paper, but for the sake of convincing myself}

\begin{lemma}\label{lem:closed-level-sets}
	Let $\Gamma$ be elicitable.
	For any $r\in\R$, the level set $\Gamma_r = \{ p \in \Delta(\Y) : \Gamma(p) = r \}$ is closed.
\end{lemma}
\begin{proof}[Proof sketch]
	Let $L$ elicit $\Gamma$.
	The function $G(p) = -\min_{r\in\R} \E_p L(r,Y) = -\E_p L(\Gamma(p),Y)$ (taking any $r\in\Gamma(p)$ in case of ties) is convex.
	There exists $\D \subseteq \partial G$ and some bijection $\varphi : \R \to \D$ with $\Gamma(p) = \varphi^{-1}(\D\cap \partial G_p)$.
	Thus, $\Gamma_r = \{p : r\in\Gamma(p)\} = \{p : \varphi(r) \in \D\cap\partial G_p\} = \{p : \varphi(r) \in \partial G_p\}$, which is closed by convex analysis.
	See [Raf/Ian\footnote{\url{https://arxiv.org/pdf/1211.3043.pdf}} (Cor 3.11), with their Thm 3.5 and Rockefellar Thm 24.4]  
\end{proof}

%\begin{definition}\label{def:unlabeled-nonredundant}
%	An unlabeled property $\Theta$ is \emph{nonredundant} if for there are no full dimensional level sets $\theta_1, \theta_2 \in \Theta$ so that $\theta_1 \subseteq \theta_2$.
%\end{definition}

\begin{lemma}\label{lem:nonempty-inter-iff-aff-ind}
	Let $\theta$ be a [closed] convex level set.
	$\theta$ is full dimensional $\iff$ there are distributions $p_1, p_2, \ldots, p_n \in \theta$ so that $p_1, p_2, \ldots, p_n$ are affinely independent.
\end{lemma}
\begin{proof}
	Recall that $n := |\Delta(\Y)|$, so we say the simplex is $n$-dimensional.
	\begin{enumerate}
		\item [$\implies$]
		Assume the level set $\theta$ is full dimensional.
		Then there exists a $p \in \inter{\theta}$ and for every $q \in B(\epsilon, p)$, we know that $q \in \theta$.
		Take $q_i = p + \epsilon e_i$\footnote{$e_i$ is the vector with $1$ in the $i^{th}$ component, and is $0$ elsewhere} in each of the $n$ dimensions, and since $\theta$ is full dimensional and closed, we know each $q_i \in\theta$.
		As $\{e_i\}_{i=1}^n$ is affinely independent (it forms the standard basis for $\reals^n$), so then is $\{q_i\}_{i=1}^n$ as we are invariant to additive and multiplicative shifts.

		\item [$\impliedby$]
		Let the set of distributions $Q := \{q_i\}_{i=1}^n$ be affinely independent, where each $q_i \in \theta$.
		Since the set $\theta$ is convex, then the convex hull $\conv(Q) \subseteq \theta$.
		It is sufficient to show $\conv(Q)$ is full dimensional.
		Let $q_1, q_2 \in Q$ so that $q_1 \neq q_2$.
		As $p = \sum_{i=1}^n \frac{1}{n}q_i \in \conv(Q)$, as is every $q \in B(\epsilon, p)$ since they are also convex combinations of elements of $Q$, we can see $\emptyset \neq \inter{\conv(Q)} \subseteq \inter{\theta}$, so we conclude $\theta$ is full-dimensional.
	\end{enumerate}
\end{proof}

@@

\begin{conjecture}\label{conj:cvx-sets-nonempty-int-iff-pos-measure}
A convex set is full-dimensional in $\reals^n$ iff it has positive Lebesgue mesaure.
\end{conjecture}
\begin{proof}

\begin{enumerate}
\item[$\implies$] A convex set that is full-dimensional contains the $\epsilon$-ball, which has positive measure. 
\item[$\impliedby$] A convex set of positive measure contains the ball, which is the superset of the convex hull of a $n$ affinely independent points, and therefore contains those points, so it is full dimensional by Lemma~\ref{lem:nonempty-inter-iff-aff-ind}.
\end{enumerate}
\end{proof}

>>>>

A set of level sets $\Theta$ is an unlabeled property, and finite if $|\Theta| < \infty$.

@@

\begin{notation}
Let $\gamma: \P \toto\R$ and $\Gamma: \P \toto\reals^d$.
We say $\gamma \preceq \Gamma$ if for all $p \in \P$, we observe $\gamma(p) = \Gamma(p) \cap \R$.
\end{notation}

\begin{definition}
	The elicitable property $\Gamma:\P\toto \reals^d$ is an \emph{d-embedding} of $\gamma: \P \toto \R$ if there exists an injection $\varphi:\R \to \reals^d$ such that $\varphi(r) \in \Gamma(p) \iff r \in \gamma(p)$. 
\end{definition}

%Note that we can take $\varphi^{-1}(r') = \{ r \in \R: \varphi(r) = r' \}$.
%That is, we define the inverse of $\varphi$ as a possibly set-valued function.

@@

\section{Lemmas on the way}

\begin{lemma}\label{lem:gam-prime-exists}
	Let $\Gamma:\P \toto \reals^d$ be a nondegenerate elicitable property with a finite set of full-dimensional level sets $\Theta$ so that $\bigcup_{\theta \in \Theta}\theta = \P$.
	There exists a nondegenerate, nonredundant property $\gamma: \P \toto \R$ such that $\gamma \preceq \Gamma$. 
\end{lemma}
\begin{proof}
	Construct the finite set $\R = \{[u] \in \Gamma(p) : p \in \inter{\theta} \}_{\theta \in \Theta}$, where $[u]$ is one consistent report for all the reports $r, r'$ such that $\Gamma_r = \Gamma_{r'}$. 
	Defining the property $\gamma : p \mapsto \Gamma(p) \cap \R$, we see that $\gamma \preceq \Gamma$.
	We want to show that the constructed $\gamma$ is nondegenerate and nonredundant.

	As $\Gamma$ is nondegenerate, there is some report $u \in \reals^d$ such that $u \in \Gamma(p)$ for all $p\in\P$, so $[u] \in \gamma(p)$ and is well-defined for all $p \in \P$.
	Thus, $\gamma$ is nondegenerate.

	To see $\gamma$ is nonredundant, first consider two reports $u_1, u_2$ such that $\Gamma_{u_1} = \Gamma_{u_2}$.
	In this case, $[u_1] = [u_2] = r$, so $\gamma_{r} = \gamma_{r}$ does not lead to a redundant report.

	\jessiet{This is the part I'm least confident about... see Lemma~\ref{lem:nonempty-inter-iff-aff-ind}}
	Now, suppose there were reports $r, r' \in \R$ so that $\gamma_{r} \subsetneq \gamma_{r'}$.
	By construction of $\R$, both $\gamma_{r'}$ and $\gamma_r$ are full dimensional.
	For each elicitable property, there is a convex scoring rule $G:\Delta_\Y \to \reals$ with a bijection between the subgradients of $G$ and reports in $\R$ (one we reduce to equivalent reports-- see Theorem~\ref{thm:bij-loss-to-score}).
	As $G$ is convex, it must be differentiable almost everywhere. 
	However, for every distribution $p \in \gamma_{r'} = \gamma_{r} \cap \gamma_{r'}$, the subgradient of $\partial G(p)$ is set-valued, and therefore $G$ is not differentiable, on this set of positive Lebesgue measure in the simplex. 
	Contradicting the elicitability of $\gamma$, we conclude $\gamma$ is nonredundant.

@@

\begin{lemma}\label{lem:define-trim}
	Let $\Gamma:\P\toto\reals^d$  be a nondegenerate, elicitable property with a finite set of level sets $\Theta$ so that $\bigcup_{\theta \in \Theta} \theta = \P$.
	There exists an unlabeled property $\Theta$ so that for all nondegenerate, nonredundant $\gamma \preceq \Gamma$, we have $\strip(\gamma) = \Theta := \trim(\Gamma)$.
\end{lemma}

\begin{proof}
	Let $\gamma:\P \toto \R$ and $\Gamma' : \P \toto \R'$ be nondegenerate, nonredundant properties so that $\gamma \preceq \Gamma$ and $\Gamma'\preceq \Gamma$.
	We want to show $\strip(\gamma) = \strip(\Gamma')$ in order to conclude that $\trim(\Gamma)$ is unique.
	For each $r \in \R$, there is a set of reports in $S \subseteq \reals^d$ so that there is a full-dimensional level set $\theta = \bigcap_{u\in S}\Gamma_s$ and $r = [u]$ for every $u \in S$.
	For the same set of reports $S$, we can equivalently choose a (possibly different) representative report $r' \in \R'$ so that $r' = [u]$ for every $u \in S$, since $\Gamma' \preceq \Gamma$.

	There is a bijection $\varphi : \R \to \R'$ so that $\varphi(\gamma(p)) = \Gamma'(p)$ for all $p \in \P$.
	Thus, the level sets of each report are the same since they are restrictions of the same property, as $\strip(\gamma) = \{ \gamma_r : r \in \R \} = \{ \Gamma_r : r \in \R \} = \{ \Gamma_{\varphi(r)} : r \in \R \} = \{ \Gamma_r : r \in \R' \} = \strip(\Gamma')$.
\end{proof}

\begin{lemma}\label{lem:lev-sets-subsets}
	Let the property $\Gamma: \P \toto \reals^d$ be elicitable and the nondegenerate, nonredundant property $\gamma: \P \toto \R$ so that $\gamma \preceq \Gamma$.
	Then the level sets of $\Gamma$ are subsets of the level sets of $\gamma$.
\end{lemma}

\begin{proof}
	It is sufficient to show $\theta \in \strip(\Gamma) \implies \theta \in \strip(\gamma)$.
	Given $\theta \in \strip(\Gamma)$, there is some report $u \in \reals^d$ so that $u \in \Gamma(p)$ for every $p \in \theta$.
	For every $r \in \R$, recall that there is an $u \in \reals^d$ so that $r = [u]$.
	By definition, $u \in \Gamma(p) \implies [u] = r \in \gamma(p)$.
	Therefore, there is some $r \in \R$ so that $p \in \Gamma_u \implies p \in \Gamma_{[u]} = \gamma_{r}$.
\end{proof}

@@

  The following are equivalent:
  \begin{enumerate}
  \item There is a nondegenerate, finite property $\gamma:\P\toto\R$ such that there is an injection $\varphi:\R\to\reals^d$ such that $r\in\gamma(p) \iff \varphi(r) \in \Gamma(p)$. (i.e. $\Gamma$ embeds finite $\gamma$).  
  \item $\trim(\Gamma)$ is finite.     
  \item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$ that union to $\P$.

  \end{enumerate}
\end{proposition}

\begin{proof}
We proceed in a cycle to show $1 \implies 2 \implies 3 \implies 1 $.
\begin{enumerate}

\item [$1 \implies 2$]

We know $\strip(\gamma) = \trim(\Gamma)$ (since $\varphi$ is an injection, and there is some intermediate property $\Gamma'$ such that $\Gamma' \preceq \Gamma$ and with a bijection $\phi:\Gamma'(p) \mapsto \gamma(p)$, so $\strip(\Gamma') = \strip(\gamma)$.) 
As $\gamma$ is finite, so is $\strip(\gamma)$ since strip is generated from the (finite) report set.

\item [$2 \implies 3$]
Since $\Gamma$ is nondegenerate and every $\theta \in \trim(\Gamma)$ is full dimensional, it is clear that the union of the (full-dimensional) level sets of $\trim(\Gamma)$ union to $\P$ by nondegneracy of $\Gamma$.

\item[$3 \implies 1$]
Construct $\R := \{[u] \in \Gamma(p) : p \in \inter{\theta} \}_{\theta \in \Theta}$.
The property $\gamma: p \mapsto \Gamma(p) \cap\R$ is then finite as $\R$ is finite.
Taking $\varphi$ to be the identity, $\Gamma$ embeds this finite $\gamma$.
\end{enumerate}

@@

\section{Lemmas probably not necessary for the paper}

\begin{lemma}\label{lem:nonempty-inter-iff-aff-ind}
	Let $\theta$ be a [closed] convex level set.
	The following are equivalent:
	\begin{enumerate}
		\item $\theta$ is full-dimensional
		\item $m(\theta) > 0$
		\item There are distributions $p_1, p_2, \ldots, p_n \in \theta$ so that $p_1, p_2, \ldots, p_n$ are affinely independent.
	\end{enumerate}
\end{lemma}
\begin{proof}
	Recall that $n := |\Delta_{\Y}|$, so we say the simplex is $n$-dimensional.
	\begin{enumerate}
		\item [$1 \implies 2$]
		A convex set that is full-dimensional contains the $\epsilon$-ball, since it has nonempty interior, and this ball has positive measure.

		\item [$2 \implies 3$]
		A convex set of positive measure contains the $\epsilon$-ball, which is the superset of the convex hull of a $n$ affinely independent points, and thus contains those points.

		\item [$3 \implies 1$]
		Let the set of distributions $Q := \{q_i\}_{i=1}^n$ be affinely independent, where each $q_i \in \theta$.
		Since the set $\theta$ is convex, then $\conv(Q) \subseteq \theta$.
		Let $q_1, q_2 \in Q$ so that $q_1 \neq q_2$.
		As $p = \sum_{i=1}^n \frac{1}{n}q_i \in \conv(Q)$, as is every $q \in B(\epsilon, p)$ since they are also convex combinations of elements of $Q$, we can see $\emptyset \neq \inter{\conv(Q)} \subseteq \inter{\theta}$, so we conclude $\theta$ is full-dimensional.
	\end{enumerate}
\end{proof}

@@
